Semantic High-definition Image Synthesis \\ with a Hierarchically-nested Adversarial Network

### 2017-10-21 cvpr2018.tex
add algorithm

% Include other packages here, before hyperref.
\usepackage{tabularx} % in the preamble
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\newcommand\VRule[1][\arrayrulewidth]{\vrule width #1}
\usepackage{array,booktabs,arydshln,xcolor} % for widening table line
\usepackage{amsthm}
\usepackage{epstopdf}
\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{amsthm}
\usepackage{multirow}
\usepackage[algo2e]{algorithm2e}
\usepackage[outercaption]{sidecap}    
\usepackage{float}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage{capt-of}% or \usepackage{caption}
\usepackage{booktabs}
\usepackage{varwidth}
\usepackage{bm}
% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[breaklinks=true,bookmarks=false]{hyperref}

@@

@@

\subsection{Preliminaries}

\subsection{Scalable Deeply Supervised}

\subsection{Functional Loss}

@@

>>>>

% Include other packages here, before hyperref.
\usepackage{tabularx} % in the preamble
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\newcommand\VRule[1][\arrayrulewidth]{\vrule width #1}
\usepackage{array,booktabs,arydshln,xcolor} % for widening table line
\usepackage{amsthm,bm}
\usepackage{epstopdf}

\usepackage{amsthm}
\usepackage{multirow}

\usepackage{float}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage{capt-of}% or \usepackage{caption}
\usepackage{booktabs}
\usepackage{varwidth}

\usepackage{algpseudocode,algorithm,algorithmicx}
\newcommand*\DNA{\textsc{dna}}

\newcommand*\Let[2]{\State #1 $\gets$ #2}
\algrenewcommand\algorithmicrequire{\textbf{Precondition:}}
\algrenewcommand\algorithmicensure{\textbf{Postcondition:}}

\makeatletter
\def\BState{\State\hskip-\ALG@thistlm}
\makeatother

\usepackage{bm}

\usepackage[breaklinks=true,bookmarks=false]{hyperref}

@@

\section{Preliminary}
\subsection{Generative Adversary Network}
Generative adversary networks (GANs) are composed of a generator $G$ and a discriminator $D$, which are alternatively trained to compete with each other in a two-player minimax game. The discriminator $D$ is optimized to distinguish the synthesized images from the real images, meanwhile, the generator $G$ is trained to fool the discriminator by trying to convert an input distribution $p_z$ to the true data distribution $p_{data}$. Concretely, the overall training procedure can be analogous to the following two-player min-max game $V(D, G)$,
 \begin{equation}
 \label{game}
 \begin{split}
  \underset{G}{\min}\ \underset{D}{\max}\ V(D, G) =  &\mathbb{E}_{x\sim p_{data}}[\log D(x)] +  \\
					  &\mathbb{E}_{z\sim p_{z}}[\log (1-D(G(z)))]		   
 \end{split}
 \end{equation}
where $x$ is a real image sampled from the true data distribution $p_{data}$, $z$ is a noise vector usually sampled from some predefined distribution $p_{z}$ (e.g., Gaussian distribution).
In practice, It's been shown to work better for the generator $G$ to minimizing $-\log(D(G(z)))$ rather than $\log(1-D(G(z)))$, namely, the $\log(D)$ trick.

Conditioned GAN \cite{isola2016image} is a variation of traditional GAN where both the generator network $G$ and discriminator network $D$ are conditioned on an additional condition vector besides the noise vector. In this paper, we consider the task of training a deep  generative adversarial network conditioned on the embedding of the text descriptions of the images.

\section{Method}
To generate high-resolution photo-realistic images from text embeddings, we propose a simple and effective multi-level Generative Adversarial Network architecture. Our model mainly consists of the following key-components,

@@

\subsection{Overview}
In this paper, we use the following notations. Denote the image dimension, text embedding dimension and the dimension of the noise input as $I$, $T$ and $Z$, respectively. for simplicity we assume the image is all square. The generator is denoted $G: \mathcal{R}^{Z}: \times \mathcal{R}^{T}\rightarrow\mathcal{R}^{I}$, the image discriminator $D_i: \mathcal{R}^{I}\rightarrow\{0, 1\}$, and the matching-aware discriminator $D_m: \mathcal{R}^{I}: \times \mathcal{R}^{T}\rightarrow\{0, 1\}$.

As is shown in Fig\ref{game}, In the generator $G$, we first sample a random vector $z\in \mathcal{R}^{Z} \scriptsize{\sim} \mathcal{N}(0,1)$, then text embedding vector $\psi{t}$ is obtained by applying an per-trained text encoder on the image description $t$, in this paper, we use the char-rnn based text encoder provided in \cite{reed2016generative}.

\textbf{Variational text encoding: } Following the work of \cite{han2017stackgan}, instead of using the plan deterministic non-linear transformation of the origin al $\Psi(t)$, we obtain the conditional vector $c$ by sampling from a Gaussian distribution $\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )$, in which the mean $\mu(\psi_t)$ and the diagonal covariance matrix $\Sigma(\psi_t)$ are non-linear transformation of the original text embedding $\psi_t$. This type of conditional augmentation technique can be used to inject randomness to the text embedding vector $\psi_t$ to mitigate the common problem that conventional conditional GAN training paradigm usually learns to $G$ that totally ignores the noise, resulting to results lacking diversity.

Conditioned on $c$ and the random vector $z$, a synthetic image $\hat{x}$ is generated as $\hat{x}\leftarrow G(c,z)$, it is simply a feed forward pass of the generator. Our generator consists of stacks of residual blocks, bilinear sampling layer is used to up-sample the feature maps.

The discriminator $D$ in our model mainly consists of two branches: matching-aware pair discrimination branch $D_{pair}$, and image discrimination branch $D_{img}$, both branches share the same  image encoder.

Given a pair of image and text embedding $(x, \psi{t})$ as input, in the discriminator $D$, we first transfer $x$  to an image code $Code_x$. $Code_x$ along with $f_{sent}(\psi_t)$ is concatenated and fed to the matching aware branch to compute a final scale value indicating the probability of the pair being real or fake, where $f_{sent}$ consists of one linear layer and one leaky ReLU transformation,  the matching-aware branch is a set of residual blocks with strid-2 convolution, more details of the architecture will be provided in the appendix. Besides that, the image code is also fed to an image-disc branch, whose structure is very similar to the matching-aware branch, to judge the probability of the input image being real or fake. We performance batch normalization on all convolutional layers. \textcolor{red}{like stackgan, I will add much more architecture details later}

The generator $G$ and discriminator $D$ are optimized alternatively using their corresponding loss function.

 \subsection{Scalable Deeply Supervised}
 \textbf{Multi-level side output:} instead of only predicting the high resolution in the final output, our model is designed to predict multi-level images of gradually increasing dimension (e.g., 256$\times$256 as the final output with 64$\times$64 and 128$\times$128 being the side output) as the side outputs. In principle, the lower-resolution side output is forced to learn the rough structure (e.g., object sketch, color information and background) of the images, the subsequent higher-resolution path is used to add more details to the images. The lower-level side output works by regularizing the lower-level image feature. Since the model is trained in an end-to-end fashion, we can observe more consistent information exhibited in both lower and higher-resolution outputs than stackGan\cite{han2017stackgan}. This type of side output is also proven useful because it allows short path between image supervision information to the hidden feature maps, which could potentially helps training.

\subsection{Generator Loss}
The generator's goal is to generator image that match the input text embedding and looks as real as possible. So the loss function for our model mainly consists of two parts, namely, matching aware loss and one image loss.  
Given a set of chosen input pair $(x, \psi_t)$, the generator is optimizing the following function
 \begin{equation}
 \label{genloss}
 \begin{split}
 \mathcal{L}_G = & \mathbb{E}_{z\sim p_{z}, t \sim p_{data}}[-\log( D_{sent}( G(z, c_t),  \psi_t) ) ] + \\
				  & \mathbb{E}_{z\sim p_{z}, t \sim p_{data}}[-\log( D_{img}( G(z, c_t) ) ) ] + \\
                  & D_{KL}(\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )|| \mathcal{N}(0, \bm{I})) 		   
 \end{split}
 \end{equation}
 where $c_t$ is the variational conditional vector generated from $\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )$. To make the network differentiable, in practice, we adopted the re-parametric trick\cite{vae}, where $c_t$ is actually computed as $\mu(\psi_t)+\Sigma(\psi_t)\odot \epsilon$, where $\epsilon\in \mathcal{R}^{T}$ is draw from a normal Gaussian distribution.

 In the spirit of variational auto-encoder, further Kullback-Leibler divergence regularization term  $D_{KL}(\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )|| \mathcal{N}(0, \bm{I}))$ is added to the final loss function to push the Gaussian distribution to the norm distribution to address over-fitting.  In addition, this term might also play a role in balancing the $c_t$ and generated condition vector $c_t$ by forcing $c$ to have a similar scale to $z$.  In the following sections, we denote $c_t$ as the variational conditional text vector.

\subsection{Functional Loss of Discriminator}
 Our goal is to generate images that not only look as realistic as real images, but also matching the given text description.
 Therefore, the discriminator must handle errors of the following two categories: real image with mismatch conditional text information, fake image with real text. In order to achieve this, the previously proposed matching aware discriminator is explicitly trained with three pair configurations, namely: real image with right text as positive training sample, and the aforementioned two sources of error pairs as negative training samples.

 Given a mini-batch of training data consists of images $x$ and the corresponding text $t$, mismatching text $\hat{t}$. First of all, we sample fakes images using $G$.
 $\hat{x_1} = G(z_1, \psi_t)$ and $\hat{x_2} = G(z_2, \psi_t)$, where $z_1$ and $z_2$ are random vector sampled from norm Gaussian distribution.

The loss function of the matching aware discriminator are summarized as:
  \begin{equation}
  \label{matchignloss}
  \begin{split}
  \mathcal{L}_D = 	  &\mathbb{E}_{(x, t) \sim p_{data}}[\log( D( x  \psi_t) ) ] -  0.5*(\\
					  &\mathbb{E}_{(x, \hat{t}) \sim p_{data}}[\log(D(x, \psi_{\hat{t}} )  ] +\\
					  &   \mathbb{E}_{t \sim p_{data}}[\log(D(\hat{x_1}, \psi_t) ) ] 
  \end{split}
  \end{equation}
This loss explicit force the discriminator to differentiate correct pair from the wrong pair.  However, there is no explicit loss that push the discriminator to differentiate real images from the fake images. The way that they formulate all the task into pair based solution complicate the task of the generator. In this paper, we propose to directly add another loss that concentrate the image quality only beside the matching loss. Specifically, it can be given by:
  \begin{equation}
  \label{discoss}
  \begin{split}
  \mathcal{L}_D = 	&\mathbb{E}_{(x, t) \sim p_{data}}[\log( D( x  \psi_t) ) ] -  0.5*(\\
		  &\mathbb{E}_{(x, \hat{t}) \sim p_{data}}[\log(D_{pair}(x, \psi_{\hat{t}} )  ] +\\
		  &\mathbb{E}_{t \sim p_{data}}[\log(D_{pair}(\hat{x_1}, \psi_t) ) ] + \\
		  &\mathbb{E}_{x \sim p_{data}}[\log( D_{img}(x) )] - 0.5* ( \\
		  &\mathbb{E}[\log( D_{img}(\hat{x_1}))] + \mathbb{E}[\log( D_{img}(\hat{x_2}) )  ] )
  \end{split}
  \end{equation}
\textcolor{red}{equations needs to be verified, just a rough place holder}

Further more, this separation of the image loss from the matching loss open further possibilities, such as utilizing the unlabeled image to improve both the genrator and discriminator. \textcolor{red}{maybe utilizing the imagenet for training the coco, or save as another paper.}

 \begin{algorithm}
 	\caption{Multi scale GAN training algorithm with step size $\alpha$, number of iteration $S$, we summarize the algorithm using SGD for simplicity.\textcolor{red}{need to change to goodfellow algorithm style}}
 	\label{CHalgorithm}
 	\begin{algorithmic}[1]

 		\For{$i \gets 1 \textrm{ to } S$ }
 		\State $z_1, z_2 \sim \mathcal{N}(0,\bm{1})^Z$
 		\State $\hat{x_1}, \hat{x_2} = G(z_1, \psi_t),  G(z_2, \psi_{\hat{t}})$ %\{Forward through $G$ using matching text embedding\}
 		\State $d_r$ = $D_{pair}(x, \psi_t)$ \{(real image, matching text)\}
 		\State $d_w$ = $D_{pair}(x, \psi_{\hat{t}})$ \{(real image, wrong text)\}
 		\State $d_f$ = $D_{pair}(\hat{x_1}, \psi_t)$ \{(fake image, matching text)\}
 		\State $s_r, s_1, s_2$ = $D_{img}(x), D_{img}(\hat{x_1})$, $D_{img}(\hat{x_1})$ %\{Forward through $D_{img}$ with $\hat{x_1}$\}

 		\State $loss_{img}$ = $ (\log(1-s_1) + \log(1-s_2))/2 $
 		\State $loss_{pair}$ = $ (\log(1-d_w) + \log(1-d_f))/2 $

 		\State $\mathcal{L}_{D}$ = $\log(d_r) + \log(s_r) +loss_{img} + loss_{pair}$
 		\State $\mathcal{L}_{G}$ = $\log(1-d_f) +  ( \log(1-s_1) + \log(1-s_2) )/2 $
 		\State $\theta_G$ = $\theta_G$ - ${\delta \mathcal{L}_G } / {\delta \theta_G}$  \{Update generator\}
 		\State $\theta_D$ = $\theta_D$ - ${\delta \mathcal{L}_D} / {\delta \theta_D}$  \{Update generator\}

 		\EndFor

 	\end{algorithmic}
 \end{algorithm}

%\begin{algorithm}
%	\caption{Multi scale GAN training algorithm with step size $\alpha$, number of iteration $S$, we summarize the algorithm using SGD for simplicity.   
%		\label{alg:gan-train}}
%	\begin{algorithmic}[1]
%		\Input{sample a minibatch of images, $x$, matching text description $t$, mis-matching $\hat{t}$,
%			}
%		\For{$i \gets 1 \textrm{ to } S$}
%			$z_1, z_2 \sim \mathcal{N}(0,\bm{1})^Z$
%			\State $\hat{x_1}$=$G(z_1, \psi_t)$ \Comment{Forward through $G$ using matching text embedding}
%			\STATE {$\hat{x_2}$}{$G(z_2, \psi_\hat{t})$} \Comment{Forward through $G$ using mis-matching text embedding}
%			
%			\STATE {$d_r$}{$D_{pair}(x, \psi_t)$} \Comment{(real image, matching text)}
%			\STATE {$d_m$}{$D_{pair}(x, \psi_\hat{t})$} \Comment{(real image, mis-matching text)}
%			\STATE {$d_f$}{$D_{pair}(\hat{x_1}, \psi_t)$} \Comment{(fake image, matching text)}
%			\STATE {$s_r$}{$D_{img}(x)$} \Comment{Forward through $D_{img}$ with $x$}
%			\STATE {$s_1$}{$D_{img}(\hat{x_1})$} \Comment{Forward through $D_{img}$ with $\hat{x_1}$}
%			\STATE {$s_2$}{$D_{img}(\hat{x_1})$} \Comment{Forward through $D_{img}$ with $\hat{x_2}$}
%			\STATE {$\mathcal{L}_{D}$}{$(d_r-1)^2 + (s_r-1)^2 + (d_m + d_f + s_1 + s2)/2 $} 
%			\STATE {$\mathcal{L}_{G}$}{$((d_f -1)^2 + (s_1 -1)^2 + (s_2 -1)^2 $} 
%			\STATE {$\theta_G$}{$\frac{\delta \mathcal{L}_G}{\delta \theta_G}$}  \Comment{Update generator}
%			\STATE {$\theta_D$}{$\frac{\delta \mathcal{L}_D}{\delta \theta_D}$}  \Comment{Update generator}
%		\EndFor	
%	\end{algorithmic}
%\end{algorithm}

@@

\section{Dataset}
